Proportional multi-state multiple-cohort life table model

### 2018-05-09 MSLT/MSLTdoc.Rmd
Added loop to generate dataframe with total outcomes

@@

## MAY NOT NEED THIS ONE
graphs_doc <- list()
index <- 1
for (age in i_age_cohort) {
      for (sex in i_sex)  {
        for (outcome in i_outcome) {

@@

```{r, echo=TRUE}
## Generate data frame with all outputs to graph total change in burden by simulation year. 
## First, need to run function for males and females separetly, in_cohorts indicates the number of age cohorts to include. To show all select 16. what is specified in in_outcomes will be graphed or can also be presented as a total.

## DO A LIST TO GENERATE ALL OUTCOMES ALL. CHECK SUMMARION OF COHORTS ORDER.

aggregate_frame_males <- gen_aggregate(in_data = output_df, in_cohorts = 16, in_population = "male", in_outcomes = c('inc_num_bl_ihd','inc_num_sc_ihd', "inc_num_diff_ihd"))

aggregate_frame_females <- gen_aggregate(in_data = output_df, in_cohorts = 16, in_population = "female", in_outcomes = c('inc_num_bl_ihd','inc_num_sc_ihd', "inc_num_diff_ihd"))

## The following adds up both males and females
## Remove non-numeric columns starting with age and sex
aggregate_frame_males <- aggregate_frame_males %>% select(-starts_with("age"), -starts_with("sex"))

aggregate_frame_females <- aggregate_frame_females %>% select(-starts_with("age"), -starts_with("sex"))

## Create a copy of aggregate_frame_females
total_aggr <- aggregate_frame_females
## Add aggregate_frame_males values to it
for (i in 1:ncol(aggregate_frame_females)){
  total_aggr[i] <- total_aggr[i] + aggregate_frame_males[i]
}
total_aggr$sim_year <- seq.int(nrow(total_aggr))
```

@@

####This plot has to be customised to in_outcomes, here, only totals shown, but specifications are up to the user

@@

disease_outcome <- "Incidence of Ischemic Heart Disease"

>>>>

# View(output_df)

@@

graphs_doc <- list()
index <- 1
for (age in i_age_cohort) {
      for (sex in i_sex)  {
        for (outcome in i_outcome) {

@@

## Try binding function

aggregate_frame_males <- list()
aggregate_frame_females <- list()

for (outcome in i_outcome) {
  for (disease in i_disease) {

aggregate_frame_males[[index]] <- gen_aggregate(in_data = output_df, in_cohorts = 16, in_population = "male", in_outcomes = c(paste(outcome, "num", "bl", disease, sep = "_"), paste(outcome, "num", "sc", disease, sep = "_"), paste(outcome, "num", "diff", disease, sep = "_")))

aggregate_frame_females[[index]] <- gen_aggregate(in_data = output_df, in_cohorts = 16, in_population = "female", in_outcomes = c(paste(outcome, "num", "bl", disease, sep = "_"), paste(outcome, "num", "sc", disease, sep = "_"), paste(outcome, "num", "diff", disease, sep = "_")))

# Remove non-numeric columns starting with age and sex
aggregate_frame_males[[index]] <- aggregate_frame_males[[index]] %>% select(-starts_with("age"), -starts_with("sex"))

aggregate_frame_females[[index]] <- aggregate_frame_females[[index]] %>% select(-starts_with("age"), -starts_with("sex"))

index <- index + 1
  }
}

## Loop for life years (Lx) and health adjusted life years (Lwx) to then add to total aggregated data.

## RUN ANOTHER LOOP FOR LX AND LWX

i_outcome2 <- c("Lx", "Lwx")

aggregate_frame_males2 <- list()
aggregate_frame_females2 <- list()

for (i in i_outcome2){

aggregate_frame_males2[[i]] <- gen_aggregate(in_data = output_df, in_cohorts = 16, in_population = "male", in_outcomes = c(paste(i, "bl", sep = "_"), paste(i, "sc", sep = "_"), paste(i, "diff",sep = "_")))

aggregate_frame_females2[[i]] <- gen_aggregate(in_data = output_df, in_cohorts = 16, in_population = "female", in_outcomes = c(paste(i, "bl", sep = "_"), paste(i,  "sc", sep = "_"), paste(i, "diff",sep = "_")))

aggregate_frame_males2[[i]] <- aggregate_frame_males2[[i]] %>% select(-starts_with("age"), -starts_with("sex"))

aggregate_frame_females2[[i]] <- aggregate_frame_females2[[i]] %>% select(-starts_with("age"), -starts_with("sex"))

## Uncomment to check data frames (list correspond to a disease and outcome combination, for example,
## incidence breast cancer)

# View(aggregate_frame_females[[2]])

## Transform list to data frame (this is not working after the first disease)

aggregate_frame_females <- do.call(cbind, aggregate_frame_females)
aggregate_frame_males <- do.call(cbind, aggregate_frame_males)
aggregate_frame_females2 <- do.call(cbind, aggregate_frame_females2)
aggregate_frame_males2 <- do.call(cbind, aggregate_frame_males2)

View(aggregate_frame_females2)

## Drop ending of variables names _males/_females to add up all outcomes in next step.

names(aggregate_frame_females) = gsub(pattern = "_female", replacement = "", x = names(aggregate_frame_females))

names(aggregate_frame_males) = gsub(pattern = "_male", replacement = "", x = names(aggregate_frame_males))

names(aggregate_frame_females2) = gsub(pattern = "_female", replacement = "", x = names(aggregate_frame_females2))

names(aggregate_frame_males2) = gsub(pattern = "_male", replacement = "", x = names(aggregate_frame_males2))

## Uncomment to check that the code is dropping the male/female ending. 
# View(aggregate_frame_males)

## Create a copy of aggregate_frame_females.  
total_aggr1 <- aggregate_frame_females
## Add aggregate_frame_males values to it
for (i in 1:ncol(aggregate_frame_females)){
  total_aggr1[i] <- total_aggr1[i] + aggregate_frame_males[i]
}

## Add data frames 2 with life years (check adds Lx and Lwx at the beginning of the variable name)
total_aggr2 <- aggregate_frame_females2
## Add aggregate_frame_males values to it
for (i in 1:ncol(aggregate_frame_females2)){
  total_aggr2[i] <- total_aggr2[i] + aggregate_frame_males2[i]
}

## Combine data frames

total_aggr <- cbind.data.frame(total_aggr1, total_aggr2)

total_aggr$sim_year <- seq.int(nrow(total_aggr))

## Uncomment to see total data frame
View(total_aggr)

## Test that total_aggr is adding males and females dataframes
# 
# (aggregate_frame_females2$Lx.Lx_bl_22 + aggregate_frame_males2$Lx.Lx_bl_22) -total_aggr$Lx.Lx_bl_22

@@

####This plot has to be customised to in_outcomes, here, only totals shown, but specifications are up to the user. ADD LOOP for all outcomes over time and total TABLE.

@@

## ADD LOOP
disease_outcome <- "Incidence of Ischemic Heart Disease"
